Computer Science House Constitution

### 2019-04-21 articles.tex
Cool
Simplify the requirements for nominations
By current practice, we don't restrict nomination only to qualified
members, so we should update that, so we can bring up candidates and
determine whether their merit should override the qualifications of a
seat.

		Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.

@@

		The Ballots will list, in random order, all of the candidates for a given office with a means to indicate the selection of one of the candidates.

@@

		Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.

>>>>

		Any House member may nominate any member or pair of members where appropriate for a Directorship.
	\item The candidates will be notified of their nomination.

@@

		The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.

@@

		Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
